Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-04-20 analysis/paper/shceof.Rmd
Elimina rmapshaper

    scale_fill_divergent_discretised("SST (K)",
                                     labels = one_less,
                                     guide = guide_colorsteps_bottom(width = 15,
                                                                     show.limits = FALSE, ticks = TRUE,
                                                                     order = 1)) +
    ggnewscale::new_scale_fill() +
    geom_contour_fill(aes(z = estimate*1e-7, fill = ..level..),
                      breaks = breaks_stream) +
    geom_contour_pval(aes(z = p_val)) +
    # geom_streamline(aes(dx = fx, dy = fy), min.L = 3, L = 10,
    #                 size = 0.1, res = 2, nx = 22, ny = 12, 
    #                 arrow.angle = 14, arrow.length = 0.2) +
    geom_vector(aes(dx = fx, dy = fy), skip = 3, min.mag = 0.002, 
                size = 0.1) +
    scale_mag(max_size = .5, guide = "none") +
    geom_qmap(keep = .015) +
    scale_fill_divergent_discretised(psi_expr, 
                                     labels = one_less,
                                     low = scales::muted("red"),
                                     high = scales::muted("blue"),
                                     guide = guide_colorsteps_bottom(15, show.limits = FALSE,
                                                                     order = 99)) +
    grid_panel(spoke, aes(angle = -angle, var = "SST"), inherit.aes = FALSE) +
    scale_x_continuous(NULL, expand = c(0, 0), 
                       breaks = seq(0, 360, by = 60),
                       labels = LonLabel) +

@@

rbind(Precipitation = pp_regr,
      `2-metre Temperature` = t2m_regr, idcol = "var") %>% 
  .[angle == 0] %>% 
  .[is.finite(r.squared)] %>% 
  # .[cEOF == "cEOF2"] %>% 
  periodic(lon = c(0, 360)) %>%
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = r.squared, fill = ..level..), breaks = breaks) +
  geom_contour_tanaka(aes(z = r.squared), breaks = breaks) +
  # geom_text_contour(aes(z = r.squared, 
  #                       label = ifelse(..level.. > 0.2, scales::percent(..level..), NA)), 
  #                   breaks = breaks, size = 2,
  #                   skip = 1, stroke = 0.15, stroke.colour = "white") +
  geom_qmap(keep = .015) +
  scale_fill_divergent_discretised(name = "Explained variance", midpoint = 0,
                                   labels = scales::percent_format(),
                                   guide = guide_colorsteps_bottom(15, show.limits = TRUE)) +

>>>>

    scale_fill_divergent_discretised("SST (K)",
                                     labels = one_less,
                                     guide = guide_colorsteps_bottom(width = 15,
                                                                     show.limits = FALSE, ticks = TRUE,
                                                                     order = 1)) +
    ggnewscale::new_scale_fill() +
    geom_contour_fill(aes(z = estimate*1e-7, fill = ..level..),
                      breaks = breaks_stream) +
    geom_contour_pval(aes(z = p_val)) +
    # geom_streamline(aes(dx = fx, dy = fy), min.L = 3, L = 10,
    #                 size = 0.1, res = 2, nx = 22, ny = 12, 
    #                 arrow.angle = 14, arrow.length = 0.2) +
    geom_vector(aes(dx = fx, dy = fy), skip = 3, min.mag = 0.002, 
                size = 0.1) +
    scale_mag(max_size = .5, guide = "none") +
    geom_qmap() +
    scale_fill_divergent_discretised(psi_expr, 
                                     labels = one_less,
                                     low = scales::muted("red"),
                                     high = scales::muted("blue"),
                                     guide = guide_colorsteps_bottom(15, show.limits = FALSE,
                                                                     order = 99)) +
    grid_panel(spoke, aes(angle = -angle, var = "SST"), inherit.aes = FALSE) +
    scale_x_continuous(NULL, expand = c(0, 0), 
                       breaks = seq(0, 360, by = 60),
                       labels = LonLabel) +

@@

rbind(Precipitation = pp_regr,
      `2-metre Temperature` = t2m_regr, idcol = "var") %>% 
  .[angle == 0] %>% 
  .[is.finite(r.squared)] %>% 
  # .[cEOF == "cEOF2"] %>% 
  periodic(lon = c(0, 360)) %>%
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = r.squared, fill = ..level..), breaks = breaks) +
  geom_contour_tanaka(aes(z = r.squared), breaks = breaks) +
  # geom_text_contour(aes(z = r.squared, 
  #                       label = ifelse(..level.. > 0.2, scales::percent(..level..), NA)), 
  #                   breaks = breaks, size = 2,
  #                   skip = 1, stroke = 0.15, stroke.colour = "white") +
  geom_qmap() +
  scale_fill_divergent_discretised(name = "Explained variance", midpoint = 0,
                                   labels = scales::percent_format(),
                                   guide = guide_colorsteps_bottom(15, show.limits = TRUE)) +
